Aa Language Reference Manual

### 2018-04-20 v2/Ahir-asm/devel/docs/AaLRM.tex
Added some dope on volatiles to the AaLRM.  Also signal read ack is always true.
Added $opaque module class to prevent spurious dependency chasing.

Complete statements can be one of the following:
\begin{itemize}
\item An {\bf assignment} statement is of the form
\begin{verbatim}
target-ref := expression
\end{verbatim}
where {\em target-ref} either specifies a declared object
or an undeclared name.  If it is an undeclared name, then
it is an implicit variable that is attached to the
assignment statement.  No other statement can write to this
variable, but any statement can read from this variable
subject to scoping rules.  Thus, every implicit variable
is such that exactly one statement defines its value.
When control flow reaches an assignment statement, it
evaluates the expression, updates the value of the target
and passes the control flow forward (we will see what this
means in the sequel).
Some examples of assignment statements are 
\begin{verbatim}
a  :=  (~b)
b  :=   (c + (d + e))
\end{verbatim}
etc.   Expressions can be {\em unary},
{\em binary} or {\em ternary}, and are
described in detail in Section \ref{sec:Expressions}.
Details of the syntax are provided in 
Section \ref{sec:Syntax}.
\item A {\bf call} statement is of the form
\begin{verbatim}
call-spec module-name input-arguments output-arguments
\end{verbatim}
The call statement thus specifies a module to which control flow
is to be passed.  The call statement may itself define new implicit
variables through its specified targets (and thus is the only
statement that can modify these newly defined implicit variables).
When control flow reaches the call statement, it forwards the
token to the called module, and finishes when the token exits
the called module.  Recursive calls and cyclical dependencies between
modules through call statements are not permitted in the \Aa language.
Here is an example of a call statement
\begin{verbatim}
// pass control to a module named foo
// foo has two inputs and three outputs
$call foo (p q)  (r s t)
\end{verbatim}
Here $p,q,r,s,t$ can be expressions.

@@

>>>>

Complete statements can be one of the following:
\begin{itemize}
\item An {\bf assignment} statement is of the form
\begin{verbatim}
target-ref := expression
\end{verbatim}
where {\em target-ref} either specifies a declared object
or an undeclared name.  If it is an undeclared name, then
it is an implicit variable that is attached to the
assignment statement.  No other statement can write to this
variable, but any statement can read from this variable
subject to scoping rules.  Thus, every implicit variable
is such that exactly one statement defines its value.
When control flow reaches an assignment statement, it
evaluates the expression, updates the value of the target
and passes the control flow forward (we will see what this
means in the sequel).
Some examples of assignment statements are 
\begin{verbatim}
a  :=  (~b)
b  :=   (c + (d + e))
\end{verbatim}
etc.   Expressions can be {\em unary},
{\em binary} or {\em ternary}, and are
described in detail in Section \ref{sec:Expressions}.
Details of the syntax are provided in 
Section \ref{sec:Syntax}.

An assignment statement can be marked as a volatile
\begin{verbatim}
$volatile a := (b+c)
\end{verbatim}
which means that $a$ will be generated from $b,c$, but
the logic which updates $a$ can be combinational.

\item A {\bf call} statement is of the form
\begin{verbatim}
call-spec module-name input-arguments output-arguments
\end{verbatim}
The call statement thus specifies a module to which control flow
is to be passed.  The call statement may itself define new implicit
variables through its specified targets (and thus is the only
statement that can modify these newly defined implicit variables).
When control flow reaches the call statement, it forwards the
token to the called module, and finishes when the token exits
the called module.  Recursive calls and cyclical dependencies between
modules through call statements are not permitted in the \Aa language.
Here is an example of a call statement
\begin{verbatim}
// pass control to a module named foo
// foo has two inputs and three outputs
$call foo (p q)  (r s t)
\end{verbatim}
Here $p,q,r,s,t$ can be expressions.

A call statement must be marked as a volatile
if the corresponding called module is volatile
\begin{verbatim}
$volatile $call foo (b c) (a)
\end{verbatim}
which means that $a$ will be generated from $b,c$, but
the logic which updates $a$ can be combinational.

@@

\subsection{Opaque Modules}

The {\bf Aa} compiler normally looks inside module
descriptions to identify load/store or pipe access
dependencies.  If you mark a module as opaque, then
the calling module will ignore dependencies inside
this module while generating the control path.

An example of an opaque module:
\begin{verbatim}
$opaque $module [foo] $in (a: $uint<9>)
   $out (b: $uint<8>) $is
{
    // out_pipe is a pipe.
    out_pipe := a

    b := in_pipe
}
\end{verbatim}
